---
title: "Sensitivity Analysis"
author: "Betsy Cowdery and Alexey Shiklomanov"
date: "4/4/2016"
output: html_document
runtime: shiny
---

This has to be run on pecan2.bu.edu to work. First, we load the PEcAn data.

```{r, results='hide'}
library(PEcAn.all)
library(ncdf4)
library(ncdf4.helpers)
pecan.id <- 1437    ## SIPNET, 500 member ensemble -- Alexey
# Some alternative ID's to choose from:
#pecan.id <- 1432    ## DALEC, 1000 member ensemble -- Betsy; original
#pecan.id <- 1436    ## DALEC, 200 member ensemble -- Alexey; more recent
#pecan.id <- 1347    ## Linkages; Ann(?); Complete ensemble analysis
output.dir <- paste0("/fs/data2/output/PEcAn_100000", pecan.id)
settings <- xmlToList(xmlParse(file.path(output.dir,"pecan.xml")))
runs <- list.files(settings$modeloutdir, full.names = TRUE)
```

Then we grab the list of output variables.

```{r}
nc <- nc_open(dir(runs[1], full.names=TRUE)[1])
vars <- nc.get.variable.list(nc)
nc_close(nc)
```

Then we source the function definitions and load the ensemble output into memory. Note that `vars` is a vector of variable names, all of which are loaded in a single command. You can pass any list of one or more variables into the `load_ensemble` function.

Also note that this takes a while and may produce a lot of text.

```{r, results='hide'}
source("load_ensemble.R")
if(file.exists("ensemble.out.RData")){
  load("ensemble.out.RData")
  } else {
  ensemble.out <- load_ensemble(outdir = output.dir, settings = settings, variable = vars)
  save("ensemble.out.RData")
}
params <- colnames(ensemble.out)[!colnames(ensemble.out) %in% vars]
```

Finally, we load the plotting functions...

```{r}
source("ensemble-plots.R")
```

...and viola! Feel free to play with this shiny magic.

```{r, echo=FALSE}
ui <- fluidPage(
  selectInput("x_select", label = "Parameter", choices = params, selected = params[2]),
  selectInput("y_select", label = "Variable", choices = vars, selected = vars[length(vars)]),
  selectInput("fitmethod_select", label = "Fit method", choices=c("lm", "spline"), selected="lm"),
  checkboxInput('pdf_select', 'Show PDFs:', TRUE),
  plotOutput("sensitivity")  
)

server <- function(input, output){
  output$sensitivity <- renderPlot({
    plot.ensemble(ensemble.out, input$x_select, input$y_select, input$pdf_select, input$fitmethod_select)
    })
  }

shinyApp(ui=ui, server=server)
```



